### 2023-05-19 paper/content.tex
Updates from Overleaf

Typically, when conducting magnetic field measurements with a large distance between the sensor and the magnetic anomaly source, higher-order non-dipole magnetization components such as quadrupoles and octupoles can be disregarded because of the strong attenuation with distance of the magnetic fields. 
However, in magnetic microscopy, where the sensor is positioned only a few microns from the sample, these higher-order components might be detected. 
This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain. 
To assess the attenuation of these non-dipolar components and the applicability of our method, we conducted simulation on particles with more complex magnetization at varying distances from the sensor.

To simulate particles with non-dipolar magnetization components, we specified a spherical volume with a radius of approximately \qty{1}{\um}. 
Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes. 
These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$, with a magnetic moment of $\qty{e-14}{\ampere\m\squared}$. 
We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$ and $y_c=\qty{25}{\um}$.
The vertical coordinate of the central position $z_c$ varied between \qty{0}{\um} and \qty{-11}{\um} in \qty{1}{\um} increments, leading to a total of 12 . By summing the $m_x$, $m_y$, and $m_z$ components of each modeled particle, we obtained the cartesian magnetization components for the spherical particle. The centroid of the particle was defined by the average of the $x_c$, $y_c$, and $z_c$ positions. The modeled vertical magnetic field was corrupted by a random noise of mean zero and a standard deviation of 20 nT.

According to Figure~\ref{non-dipolarity-synthetic-data} obtained from this simulation, it can be observed that when the particle is very close to the sensor, there is a strong non-dipolar contribution (Figure~\ref{non-dipolarity-synthetic-data}a-b) characterized by low $R^2$ values. As the distance increases, the magnetic signal is strongly attenuated, especially the non-dipolar components that decay more rapidly than the dipolar component, resulting in a rapid increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). At distances above 5 $\mu$m, there is practically only the contribution of the dipolar component, causing $R^2$ values to be very close to 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).

@@

To assess the algorithm's capability to handle particles with more complex magnetization, we replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough to emphasize the contribution from higher-order components, a lower degree of dipolarity is observed as expressed by lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).

>>>>

Typically, when conducting magnetic field measurements with a large distance between the sensor and the magnetic anomaly source, higher-order non-dipole magnetization components such as quadrupoles and octupoles can be disregarded because of the strong attenuation with distance of the magnetic fields. 
However, in magnetic microscopy, where the sensor is positioned only a few microns from the sample, these higher-order components might be detected. 
This phenomenon is observed in paleomagnetic studies on particles with a PSD domain state, where magnetization is non-uniform throughout the grain. 
To assess the attenuation of these non-dipolar components and the applicability of our method, we conducted a simulation on particles with more complex magnetization at varying sensor-sample distances.

To simulate particles with non-dipolar magnetization components, we specified a spherical volume with a radius of approximately \qty{1}{\um}. 
Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes. 
These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$ and with standard deviation of \ang{10}.
The dipole moment amplitudes were sampled by a normal distribution with mean $\qty{e-14}{\ampere\m\squared}$ and standard deviation $\qty{5e-14}{\ampere\m\squared}$. 
We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$, $y_c=\qty{25}{\um}$, and $z_c=\qty{-1}{\um}$ with standard deviation of \qty{0.65}{\um}.
The bulk magnetization of the non-dipolar particle is the vector sum of the dipole moments of each dipole. 
The centroid of the particle is defined by the average of the $x_c$, $y_c$, and $z_c$ positions of each dipole.
The synthetic vertical magnetic field $b_z$ of the non-dipolar source was calculated on regular grids with \qty{0.5}{\um} spacing.
Each grid was located at a different sensor-sample distance $z$, varying between \qty{1}{\um} and \qty{10}{\um} in \qty{0.5}{\um} increments. 
The synthetic data were corrupted by pseudo-random gaussian noise of mean \qty{0}{\nano\tesla} and a standard deviation of \qty{20}{\nano\tesla}.
For each data grid generated, we performed Euler deconvolution to estimate the source position and subsequently inverted the data for the dipole moment.
At each step, we recorded the inversion $R^2$ value and the differences between the estimated position and dipole moment and the true centroid and bulk magnetization of the particle.

Figure~\ref{non-dipolarity-synthetic-data} shows the synthetic $b_z$ of an example non-dipolar particle at variable source-sample distances.
When the particle is close to the sensor (\qty{1-3}{\um}), the observed field is strongly non-dipolar (Figure~\ref{non-dipolarity-synthetic-data}a-b) and the dipole moment inversion produces low $R^2$ values. 
As the distance increases, the magnetic field is attenuated, particularly the non-dipolar components which decay more rapidly than the dipolar component.
This results in an increase in $R^2$ (Figure~\ref{non-dipolarity-synthetic-data}c-d). 
At distances above \qty{5}{\um}, there is practically only the contribution of the dipolar component, causing $R^2$ to approach its maximum value of 1 (Figure~\ref{non-dipolarity-synthetic-data}e-f).

@@

We replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough to emphasize the contribution from higher-order components, a lower degree of dipolarity is observed as expressed by lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).
